---
title: "HW3"
author: "Nora Murray"
date: "10/04/2019"
---
```{r setup, include=FALSE}
require(rgdal)
require(leaflet)
require(leaflet.extras)

require(dplyr)
require(readxl)
require(stringr)
require(geojsonio)
library(RColorBrewer)
library(tidycensus)
library(tigris)

```
```
```
# Load Data for Point Base Map: Mobile Home Data
<br>
source: https://hifld-geoplatform.opendata.arcgis.com/datasets/mobile-home-parks
<br>
<br>
Using data from the US Department of Homeland Security, I have plotted locations of trailer parks across New York State. It appears most trailer parks have fewer than 50 trailers and are unsurprisingly concentrated Upstate.
<br>

```{r echo=FALSE, results='hide'}

# Load mobile home data

mobile_home_df <- data.frame(read.csv("Mobile_Home_Parks.csv"))

#Subset NY Data 

mobile_home_ny <- subset(mobile_home_df, STATE == "NY")

#Data Exploration

dim(mobile_home_ny)
names(mobile_home_ny)

```

<br>
# Marker Point Map
<br>

```{r}
# Load mobile home data
pal <- colorFactor(c("mediumturquoise",  "purple" , "cadetblue4" ), domain = c("LARGE (>100)", "MEDIUM (51-100)","SMALL (<50)"))

basemap_points <-leaflet(mobile_home_ny) %>%
  # Basemaps
  addTiles()%>%
  addProviderTiles("Esri.WorldPhysical", group = "WorldPhysical") %>%
  addCircleMarkers(group = mobile_home_ny$SIZE, stroke = F, color = ~pal(SIZE), weight = 50,
                   fillOpacity = 0.5) %>%
    addLayersControl(
    baseGroups = c("OSM (default)", "WorldPhysical"),
    overlayGroups = c(levels(mobile_home_ny$SIZE)),
    options = layersControlOptions(collapsed = FALSE))%>%
   addLegend("bottomright", pal = pal, values = ~SIZE,
    title = "Size of Mobile Home Community")

basemap_points %>% 
  fitBounds(-78, 45, -72, 40) # Fit to NY

```
<br>
# Data from : https://hifld-geoplatform.opendata.arcgis.com/datasets/public-transit-routes/data?geometry=-104.352%2C31.109%2C-57.023%2C43.309
<br>

## Public Transit Data from DHS
<br>

This plot shows the public transit systems and the system authority under which the transit system runs under. 
Again, most of these transit systems are concentrated in New York City, with a very small transit line in Buffalo. 

```{r}
# LINE PLOT

# Load Shape File 
public_transit <- readOGR("Public_Transit_Routes.shp")

# Limit to NY Transit Systems
ny_lines <- c("METRO-NORTH COMMUTER RAILROAD COMPANY, DBA: MTA METRO-NORTH RAILROAD",  
              "MTA LONG ISLAND RAIL ROAD",                                                                  
              "MTA NEW YORK CITY TRANSIT",                                                                  
              "NIAGARA FRONTIER TRANSPORTATION AUTHORITY",                                                  
              "PORT AUTHORITY OF NEW YORK AND NEW JERSEY",                                                  
              "PORT AUTHORITY TRANS-HUDSON CORPORATION",                                                    
              "STATEN ISLAND RAPID TRANSIT OPERATING AUTHORITY, DBA: MTA STATEN ISLAND RAILWAY")

public_transit_ne <- subset(public_transit, public_transit$SYS_AGENCY %in% ny_lines)

#Create Color Pallette

cols <- colorRampPalette(brewer.pal(8,"Dark2"))(length(ny_lines))
pal2 <-colorFactor(cols, domain = ny_lines)

leaflet(data = public_transit_ne) %>%
  # Basemaps
  addTiles() %>%
  addProviderTiles("Esri.WorldGrayCanvas", group = "WorldGrayCanvas") %>%
  addProviderTiles("Esri.WorldTerrain", group = "WorldTerrain") %>%
  addPolylines(group = public_transit_ne$SYS_AGENCY, color = ~pal2(SYS_AGENCY))  %>%
  # Layers control
  addLayersControl(
    baseGroups = c("WorldGrayCanvas", "WorldTerrain"),
    # overlayGroups = ne_lines,
    # position = "bottomleft",
    options = layersControlOptions(collapsed = FALSE)) %>%
   addLegend("topright", pal = pal2, values = ~SYS_AGENCY,
    title = " New York Public Transit Lines By System")  %>%
    fitBounds(-79, 48, -72, 39) # Fit to Northeast


                 

```

# Polygon Map with 2 Layers 
<br>
Given that we know there are more mobiles homes Upstate and more transit lines downstate, one might infer that Downstate is where the population center is.  
<br>
<br>
If Downstate has more transit lines, do they use fewer cars or does the difference in population outweight this? 
Based on this map, we conclude that Downstate has a much larger population and the different of population means more cares, irrespective of public transit. 
<br>

#Prep the data and add shapefile 
<br>
Data source: https://www.census.gov/data.html

```{r, results='hide'}
# Source: https://walkerke.github.io/tidycensus/reference/load_variables.html
# Get the data from the census

v17 <- load_variables(2017, "acs5", cache = TRUE)

# Vehicle Ownership 
ny_data_car <- get_acs(geography = "county", 
                       variables = c("B08541_006"),
                       state = 36,
                       geometry = FALSE)
# Population
ny_data_pop <- get_acs(geography = "county", 
                       variables = c("B01003_001"),
                       state = 36,
                       geometry = FALSE)

# Get NYS county shapefile 
ny_counties <- counties(state = 36)


# Merge Car and Population data files in a single file 

poly_map_data <- merge(ny_data_car, ny_data_pop, by = c("GEOID", "NAME"), sort = FALSE)

ny_counties@data<- merge(ny_counties@data, poly_map_data, by = c("GEOID"), sort = FALSE)

#Merge Car and Shapefile data
cars_ny <- merge(ny_counties, ny_data_car, by = c("GEOID"))


# Recall Varible x is car data and variable.y is population data 


```

# Polygon Map with Number of Cars and Number of People

```{r}

# Palette for Number of Cars 
pal_car <- colorNumeric(
  palette = "Reds",
  na.color = "#808080",
  domain = ny_counties$estimate.x)  # of Cars 

# Palette for Population
pal_ppl <- colorNumeric(
  palette = "Purples",
  na.color = "#808080",
  domain = ny_counties$estimate.y)  # population 

basemap_poly <- leaflet(ny_counties) %>%
  addTiles() %>%
  addProviderTiles("Esri.WorldGrayCanvas", group = "WorldGrayCanvas") %>%
  addProviderTiles("CartoDB.Positron", group = "Positron") %>%
    fitBounds(-79, 45, -72, 39) # Fit to Northeast

basemap_poly %>%
  addPolygons(
        color = ~pal_car(estimate.x),
        stroke = FALSE,
        weight = 2,
        opacity = 1,
        dashArray = "3",
        fillOpacity = 0.7, 
        group = "Number of Cars") %>%
            addLegend(group = "Number of Cars", "bottomright", 
                      pal = pal_car, values = ny_counties$estimate.x, 
                      data = getMapData(basemap_poly),title = "Number of Cars") %>%
  addPolygons(
        color = ~pal_ppl(estimate.y),
        stroke = FALSE,
        weight = 2,
        opacity = 1,
        dashArray = "3",
        fillOpacity = 1, 
        group = "Number of People")%>%
            addLegend(group = "Number of People", "bottomright", 
                      pal = pal_ppl, values = ny_counties$estimate.y, 
                      data = getMapData(basemap_poly), title = "Number of People") %>%
  addLayersControl(
      baseGroups = c("WorldGrayCanvas", "Positron"),
      overlayGroups = c("Number of Cars", "Number of People"),
      options = layersControlOptions(collapsed = FALSE)) %>% 
  hideGroup("Number of People")


  

```

